\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-04-30 Thesis.tex
adding thesiss

\documentclass[twoside, 12pt]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
%\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.2} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usepackage[section]{placeins}
\usepackage{nameref}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\usepackage{eurosym}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{assets/Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{The Combination of Spatial Narrative and Semantic Closeness to derive Visualizations of Theory Graphs}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis Proposal in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

@@

\newpage
\noindent
  With my signature, I certify that this thesis proposal has been written by me
  using only the indicated resources and materials. Where I have
  presented data and results, the data and results are complete,
  genuine, and have been obtained by me unless otherwise acknowledged;
  where my results derive from computer programs, these computer
  programs have been written by me unless otherwise acknowledged. I
  further confirm that this thesis has not been submitted, either in
  part or as a whole, for any other academic degree at this or another
  institution.

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context. The proposed research aims at taking an existing annotated corpus and presenting its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge should enable users to interactively examine materials that are related to the topics the audience is interested in.\\

@@

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, the proposed research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. If this approach proves successful it will transform how we interact with course material and learning processes in general. Ultimately, this research may be applicable to almost all areas in which knowledge needs to be transferred.\\

@@

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through adding context, to not just provide information, but rather knowledge.\\

The concept behind these two developments is quite similar. Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content. While this led to a lot of information on the web, it provided comparatively little knowledge. Here the processing of information to provide knowledge is lacking. Similarly, the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format. As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but often lack structure and context.\\

In essence, both issues stem from information being generated without enough context or structure. This makes the information hard to process by humans and/or machines. The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer. The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

@@

One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer. Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information. From information, we can then obtain knowledge through adding networking.\\

We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of. In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e. the context the information is a part of. Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\

To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks). For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents. This will give us information about the semantic closeness of different pieces of information. Taking this as a starting point, we will visualize the dependencies of the information contained in these documents. Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative with the help of a presentation framework such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\

@@

To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time. There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole. \\

@@

To understand the problem of information that lacks context, this part of the proposal will provide the necessary background information. It will allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively. While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

@@

In this section we will introduce some basic terminology which will be needed to discuss the actual subject matter in the following part. We will conceptualize what we mean by the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\

The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}. For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". This \textit{association} is of special importance for the current project. We will define it as knowledge that is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure \ref{fig:Annie-presentation-information}).\\

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Information in context}
  \label{fig:Annie-context}
\vspace{-10pt}
\end{wrapfigure}

According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning". Context can be easily explained with the example of Annie learning the Pythagorean theorem. The \textit{information} about the calculation of the length of the third side of the triangle is only helpful for Annie within the \textit{context} of the pieces of \textit{information} this depends on. Without this \textit{context}, Annie cannot understand the theorem. Figure \ref{fig:Annie-context} illustrates the context by showing the dependencies of the theorem, i.e. calculating squares, area calculation, triangles, and right angles. It semiotically represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}. We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\

\subsection{OMDoc}
\label{sec:OMDoc}

OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents. As such it is a semi-formal domain ontology. An ontology provides the framework for creating a semantic structure. It formally describes concepts within a specified area. A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given. The semi-formal ontology can consist of partial or incomplete knowledge. \\

If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways. This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts. The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations. This elevates the net of separate pieces of information that are stored individually to a semantic representation and one step further to knowledge.\\

\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.48\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

In \textit{A mathematical approach to ontology authoring and
documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. These levels of semantic closeness are represented through the different sizes of the frames of the related information. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness of content. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}

In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

@@

In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced. In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced. These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}. The accessibility depends on the relative \textit{newness}, i.e. recency of mention, of this information.\\

These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class. In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}. Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}. We will additionally introduce a third modus for information called \textit{course-ancient}. This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e. \textit{course-ancient}.\\

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4xml3ancient}
    }
  \end{center}
\vspace{-20pt}
  \caption{Course-ancient information}
  \label{fig:Annie-ancient}
\vspace{-10pt}
\end{wrapfigure}

Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}. The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}. This is marked orange in figure \ref{fig:Annie-ancient}. The information about squares which Annie still remembers is \textit{course-old}. Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course. \\

\subsection{Different Representations of Information}
\label{sec:inforep}

Information can be (re)presented in different ways: text, visuals, images, etc. Actually everything that is in the world around us conveys information to us. A sign of a women on a door conveys to most of us that this is a bathroom for women. The information graphs that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a person to process. Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. \\

In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door. We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\

@@

Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\

These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly, we will employ visual relations as in figure \ref{fig:rel_objects} to show related content. Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts. Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\

@@

Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures. The frames can be mapped directly to the nodes/concepts that graphs use. Text and images are taken for granted within the frames. Similarly, the visual relation between different frames is very much like the relations between nodes. However, the relations can be much more expressive within Impress.js.\\

Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information. Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for interactiveness.\\

>>>>

\documentclass[twoside, 12pt]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.2} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usepackage[section]{placeins}
\usepackage{nameref}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\usepackage{eurosym}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{assets/Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Theory Graphs}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

@@

\newpage
\noindent
  With my signature, I certify that this thesis has been written by me
  using only the indicated resources and materials. Where I have
  presented data and results, the data and results are complete,
  genuine, and have been obtained by me unless otherwise acknowledged;
  where my results derive from computer programs, these computer
  programs have been written by me unless otherwise acknowledged. I
  further confirm that this thesis has not been submitted, either in
  part or as a whole, for any other academic degree at this or another
  institution.

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context. The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge enable susers to interactively examine materials that are related to the topics the audience is interested in.\\

@@

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research presents different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning while discussing several different schema that are ditaktisch wertvoll\ednote{check translation}.This approach to presenting learning materials changes how we interact with course material which will allow students to learn better. Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\

@@

%The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through adding context, to not just provide information, but rather knowledge.\\

%The concept behind these two developments is quite similar. Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content. While this led to a lot of information on the web, it provided comparatively little knowledge. Here the processing of information to provide knowledge is lacking. Similarly, the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format. As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but often lack structure and context.\\

%In essence, both issues stem from information being generated without enough context or structure. This makes the information hard to process by humans and/or machines. The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer. The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

@@

%One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer. Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information. From information, we can then obtain knowledge through adding networking.\\

%We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of. In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e. the context the information is a part of. Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\

%To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks). For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents. This will give us information about the semantic closeness of different pieces of information. Taking this as a starting point, we will visualize the dependencies of the information contained in these documents. Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative with the help of a presentation framework such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\

@@

%To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

%After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time. There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole. \\

@@

As we have pointed out in the \ref{sec:introduction}, presenting information in an efficient way is essential in order for any learning to occur. In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how Annie's teacher can transfer knowledge more effectively.\\

@@

Before discussing the buzzword knowledge transfer further, we will first engage in the conceptualization of the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\

%The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}. For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". This \textit{association} is of special importance for the current project. We will define it as knowledge that is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure \ref{fig:Annie-presentation-information}).\\

\ednote{In current presentations there is only one context. By adding more levels of context we can allow viewers to understand the subject on a deeper level.}

%According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning". Context can be easily explained with the example of Annie learning the Pythagorean theorem. The \textit{information} about the calculation of the length of the third side of the triangle is only helpful for Annie within the \textit{context} of the pieces of \textit{information} this depends on. Without this \textit{context}, Annie cannot understand the theorem. Figure \ref{fig:Annie-context} illustrates the context by showing the dependencies of the theorem, i.e. calculating squares, area calculation, triangles, and right angles. It semiotically represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}. We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
\newpage
\subsection{OMDoc}
\label{sec:OMDoc}

%OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents. As such it is a semi-formal domain ontology. An ontology provides the framework for creating a semantic structure. It formally describes concepts within a specified area. A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given. The semi-formal ontology can consist of partial or incomplete knowledge. \\

%If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways. This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts. The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations. This elevates the net of separate pieces of information that are stored individually to a semantic representation and one step further to knowledge.\\

%In \textit{A mathematical approach to ontology authoring and documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. These levels of semantic closeness are represented through the different sizes of the frames of the related information. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness of content. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
\newpage
\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}

%In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

@@

%In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced. In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced. These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}. The accessibility depends on the relative \textit{newness}, i.e. recency of mention, of this information.\\

%These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class. In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}. Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}. We will additionally introduce a third modus for information called \textit{course-ancient}. This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e. \textit{course-ancient}.\\

%Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}. The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}. This is marked orange in figure \ref{fig:Annie-ancient}. The information about squares which Annie still remembers is \textit{course-old}. Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course. \\
\newpage
\subsection{Different Representations of Information}
\label{sec:inforep}

%Information can be (re)presented in different ways: text, visuals, images, etc. Actually everything that is in the world around us conveys information to us. A sign of a women on a door conveys to most of us that this is a bathroom for women. The information graphs that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a person to process. Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. \\

%In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door. We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\

@@

%Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\

%These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly, we will employ visual relations as in figure \ref{fig:rel_objects} to show related content. Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts. Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\

@@

%Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

%Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

%For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures. The frames can be mapped directly to the nodes/concepts that graphs use. Text and images are taken for granted within the frames. Similarly, the visual relation between different frames is very much like the relations between nodes. However, the relations can be much more expressive within Impress.js.\\

%Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information. Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for interactiveness.\\

%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\
\newpage
\subsection{Spatial Narrative}
\label{sec:spatialnarrative}
